Word learning at the semantics pragmatics interface

### 2020-04-01 paper/supplementary_material.Rmd
play around with visuals

To decide between referents, the listener reasons about what a rational speaker would say given an intended referent. This speaker is assumed to compute the informativity of for each available utterance and then choose the most informative one. However, this expectation of speaker informativeness may vary and is captured by the parameter $\alpha$. In particular, we take $\alpha$ to be a function of the child's age.

@@

ggplot(data = plot_cor_model_pred,aes(x = model_mean, y = data_mean, col = alignment)) +
  geom_abline(intercept = 0, slope = 1, lty = 2, alpha = 1, size = .5)+
  geom_errorbar(aes(ymin = data_ci_lower, ymax = data_ci_upper),width = 0,size = .5, alpha = .7)+
  geom_errorbarh(aes(xmin = model_ci_lower, xmax = model_ci_upper), height = 0,size = .5, alpha = .7)+
  geom_point(size = 1.5, stroke = 1, pch = 5)+
  coord_fixed()+
 stat_cor(method = "pearson", label.x = 0.01, label.y = 0.99, aes(x = model_mean, y = data_mean), inherit.aes = F, size = 3)+
  xlim(0,1)+ylim(0,1)+
  xlab("Model")+
  ylab("Data")+
  facet_grid(age~model)+
  theme_few() + 
  scale_colour_ptol(name ="Condition")
```

@@

ggplot(data = plot_cor_model_exp,aes(x = model_mean, y = data_mean, col = alignment)) +
  geom_abline(intercept = 0, slope = 1, lty = 2, alpha = 1, size = .5)+
  geom_errorbar(aes(ymin = data_ci_lower, ymax = data_ci_upper),width = 0,size = .5, alpha = .7)+
  geom_errorbarh(aes(xmin = model_ci_lower, xmax = model_ci_upper), height = 0,size = .5, alpha = .7)+
  geom_point(size = 1.5, stroke = 1, pch = 5)+
  coord_fixed()+
 stat_cor(method = "pearson", label.x = 0.01, label.y = 0.99, aes(x = model_mean, y = data_mean), inherit.aes = F, size = 3)+
  xlim(0,1)+ylim(0,1)+
  xlab("Model")+
  ylab("Data")+
  facet_grid(age~model)+
  theme_few() + 
  scale_colour_ptol(name ="Condition")
```

>>>>

To decide between referents, the listener reasons about what a rational speaker would say given an intended referent. This speaker is assumed to compute the informativity for each available utterance and then choose the most informative one. However, this expectation of speaker informativeness may vary and is captured by the parameter $\alpha$. In particular, we take $\alpha$ to be a function of the child's age.

@@

ggplot(data = plot_cor_model_pred,aes(x = model_mean, y = data_mean, col = alignment)) +
  geom_abline(intercept = 0, slope = 1, lty = 2, alpha = 1, size = .5)+
  geom_errorbar(aes(ymin = data_ci_lower, ymax = data_ci_upper),width = 0,size = .5, alpha = .7)+
  geom_errorbarh(aes(xmin = model_ci_lower, xmax = model_ci_upper), height = 0,size = .5, alpha = .7)+
  geom_point(size = 1.5, stroke = 1, pch = 5)+
  coord_fixed()+
stat_cor(method = "pearson", label.x = 0.01, label.y = 0.99, aes(x = model_mean, y = data_mean, label = paste(..rr.label..)), inherit.aes = F, size = 3)+
  xlim(0,1)+ylim(0,1)+
  xlab("Model")+
  ylab("Data")+
  facet_grid(age~model)+
  theme_few() + 
  scale_colour_ptol(name ="Condition")
```

@@

ggplot(data = plot_cor_model_exp,aes(x = model_mean, y = data_mean, col = alignment)) +
  geom_abline(intercept = 0, slope = 1, lty = 2, alpha = 1, size = .5)+
  geom_errorbar(aes(ymin = data_ci_lower, ymax = data_ci_upper),width = 0,size = .5, alpha = .7)+
  geom_errorbarh(aes(xmin = model_ci_lower, xmax = model_ci_upper), height = 0,size = .5, alpha = .7)+
  geom_point(size = 1.5, stroke = 1, pch = 5)+
  coord_fixed()+
stat_cor(method = "pearson", label.x = 0.01, label.y = 0.99, aes(x = model_mean, y = data_mean, label = paste(..rr.label..)), inherit.aes = F, size = 3)+
  xlim(0,1)+ylim(0,1)+
  xlab("Model")+
  ylab("Data")+
  facet_grid(age~model)+
  theme_few() + 
  scale_colour_ptol(name ="Condition")
```

### 2020-04-01 paper/visualizations.Rmd
play around with visuals

```{r, include = F}
library(tidyverse)
library(rwebppl)
library(gridExtra)
library(coda)
library(ggthemes)
library(readxl)
library(ggpubr)
library(stringr)
library(matrixStats)
library(data.table)
library(langcog)
library(ggimage)
library(BayesFactor)

@@

sem_know_map <- item_params_summary%>%
  select(-uci,-lci)%>%
  spread(parameter, -item) %>%
  expand_grid(., age = unique(me_data$age)) %>%
  mutate(sem_know = plogis(intercept + slope * age)) %>%
  left_join(aoa_ratings) %>%
  ungroup()%>%
  mutate(item = fct_reorder(factor(item), mean_aoa))

plot_sem_know <- ggplot()+
  geom_line(data = sem_know_map, aes(x = age+2, y= sem_know, col = item, group = item),size = 1)+
  ylab("Semantic knowledge")+
  xlab("Age")+
  ylim(0,1)+
  theme_few()+
  scale_colour_viridis_d(name = "Object")

# plot or speaker optimality

@@

plot_speak_opt <- ggplot() +
  geom_line(data = speak_opt_line, aes(x=age+2,y = y, group = interaction(chain,iteration)), size = .2, alpha = .1)+
  geom_line(data = speak_opt_map, aes(x=age+2,y = y),size = 1)+
  labs(x="Age",y="Speaker informativeness")+
  theme_few() +
  ylim(0,10)+
    xlim(2,5)+
  guides(alpha = F, fill = F, col = F)

@@

plot_prior <- ggplot() +
  geom_line(data = prior_line, aes(x=age+2,y = y, group = interaction(chain,iteration)), size = .2, alpha = .1)+
  geom_line(data = prior_map, aes(x=age+2,y = y),size = 1)+
  labs(x="Age",y="Prior sensitivity")+
  theme_few() +
  ylim(0,1)+
  xlim(2,5)+
  guides(alpha = F, fill = F, col = F)

```
```{r}
plot_cor_model_pred <- readRDS( "../saves/corr_model_data_pred.rds")%>%
  mutate(model = factor(model, levels = c("integration", "no word knowledge", "no common ground", "no mutual exclusivity")))%>%
  filter(model == "integration")

pred_cor <- ggplot(data = plot_cor_model_pred,aes(x = model_mean, y = data_mean, col = alignment)) +
  geom_abline(intercept = 0, slope = 1, lty = 2, alpha = 1, size = .5)+
  geom_errorbar(aes(ymin = data_ci_lower, ymax = data_ci_upper),width = 0,size = .5, alpha = .7)+
  geom_errorbarh(aes(xmin = model_ci_lower, xmax = model_ci_upper), height = 0,size = .5, alpha = .7)+
  geom_point(size = 1.5, stroke = 1, pch = 5)+
  #coord_fixed()+
 stat_cor(method = "pearson", label.x = 0.01, label.y = 0.99, aes(x = model_mean, y = data_mean), inherit.aes = F, size = 3)+
  xlim(0,1)+ylim(0,1)+
  xlab("Model")+
  ylab("Data")+
  facet_grid(~age)+
  theme_few() + 
  scale_colour_ptol(name ="Condition")
```

@@

>>>>

```{r, include = F}
library(tidyverse)
library(rwebppl)
library(gridExtra)
library(coda)
library(ggthemes)
library(readxl)
library(ggpubr)
library(stringr)
library(matrixStats)
library(data.table)
library(langcog)
library(ggimage)
library(BayesFactor)
library(xkcd)

@@

sel_items <- c("apple", "pawn", "garlic", "bread")

sem_know_map <- item_params_summary%>%
  filter(item %in% sel_items)%>%
  select(-uci,-lci)%>%
  spread(parameter, -item) %>%
  expand_grid(., age = unique(me_data$age)) %>%
  mutate(sem_know = plogis(intercept + slope * age)) %>%
  left_join(aoa_ratings) %>%
  ungroup()%>%
  mutate(item = fct_reorder(factor(item), mean_aoa))

plot_sem_know <- ggplot()+
  geom_line(data = sem_know_map, aes(x = age+2, y= sem_know, col = item, group = item),size = 1)+
  ylab("Semantic knowledge")+
  xlab("Age")+
  theme_xkcd()+ 
  scale_y_continuous(
    breaks = c(0,0.9),
    labels= c("no idea", "very sure"))+
  guides(col = guide_legend(title="Object"))

```{r}
# plot or speaker optimality

@@

plot_speak_opt <- ggplot() +
  #geom_line(data = speak_opt_line, aes(x=age+2,y = y, group = interaction(chain,iteration)), size = .2, alpha = .1)+
  geom_line(data = speak_opt_map, aes(x=age+2,y = y),size = 1)+
  labs(x="Age",y="Speaker informativeness")+
    xlim(2,5)+
  guides(alpha = F, fill = F, col = F)+
  theme_xkcd()+
  scale_y_continuous(
    limits = c(1,6),
    breaks = c(1,6),
    labels= c("OK", "very high"))

@@

plot_prior <- ggplot() +
  #geom_line(data = prior_line, aes(x=age+2,y = y, group = interaction(chain,iteration)), size = .2, alpha = .1)+
  geom_line(data = prior_map, aes(x=age+2,y = y),size = 1)+
  labs(x="Age",y="Sensitivity to common ground")+
  xlim(2,5)+
  guides(alpha = F, fill = F, col = F)+
  theme_xkcd()+
  scale_y_continuous(
    limits = c(0.5,1),
    breaks = c(0.5,1),
    labels= c("absent", "high"))

```{r}
ggsave(plot = plot_speak_opt,"../graphs/speak_inf.png", width = 2.5, height = 2.5, scale = 1.5)
```

ggplot(data = comb_data, aes(x = age_num, y = correct)) +
  #geom_hline(yintercept = 0.5, lty=2)+
  #geom_jitter(col = "black", height = .025, alpha = .1)+
  #geom_pointrange(data = comb_data_binned, aes(x = subage+.5, y = data_mean, ymin =data_ci_lower, ymax = data_ci_upper), stroke = 1, pch = 5)+
  #geom_line(data = comb_data_binned, aes(x = subage+.5, y = data_mean))+
  geom_line(data = plot_prag_pred, aes(x=age+2,y = pred, col = alignment, group = interaction(chain,iteration)), size = .2, alpha = .25)+
  #geom_smooth(data = comb_data, aes(x = age_num, y = correct), col = "black", method = "glm", method.args = list(family = "binomial"), se = T, alpha = .4, lty = 2, size = 1)+
  labs(x="Age",y="Mutual Exclusivity effect")+
  facet_grid(alignment~item)+
  theme_few() +
  ylim(-0.05,1.05)+
  xlim(2,5)+
  theme_xkcd()+
  guides(alpha = F, fill = F, col = F)+
  scale_y_continuous(
    limits = c(0,1),
    breaks = c(0,1),
    labels= c("low", "high"))
```

```{r}
ggsave("../graphs/pred_cartoon.png", width = 7.5, height = 2, scale = 1.5)
```

```{r}
plot_cor_model_pred <- readRDS( "../saves/corr_model_data_pred.rds")%>%
  mutate(model = factor(model, levels = c("integration", "no word knowledge", "no common ground", "no mutual exclusivity")))%>%
  filter(model == "integration")

pred_cor <- ggplot(data = plot_cor_model_pred,aes(x = model_mean, y = data_mean)) +
  geom_abline(intercept = 0, slope = 1, lty = 2, alpha = 1, size = .5)+
  geom_errorbar(aes(ymin = data_ci_lower, ymax = data_ci_upper),width = 0,size = .5, alpha = .7)+
  geom_errorbarh(aes(xmin = model_ci_lower, xmax = model_ci_upper), height = 0,size = .5, alpha = .7)+
  geom_point(size = 1.5, stroke = 1, pch = 5)+
  coord_fixed()+
 stat_cor(method = "pearson", label.x = 0.01, label.y = 0.99, aes(x = model_mean, y = data_mean, label = paste(..rr.label..)), inherit.aes = F, size = 3)+
  xlim(0,1)+ylim(0,1)+
  xlab("Model")+
  ylab("Data")+
  facet_grid(~age)+
  theme_few() + 
  theme(legend.position = c(.9,.2), 
        legend.background = element_blank())
```

```{r}
ggsave(plot = pred_cor,"../graphs/cor_pred.png", width = 6, height = 2, scale = 1.5)
```

@@

```{r}
plot_prag_exp<- readRDS( "../saves/plot_prag_exp.rds")

ggplot(data = comb_data, aes(x = age_num, y = correct)) +
  geom_hline(yintercept = 0.5, lty=2)+
  #geom_jitter(col = "black", height = .025, alpha = .1)+
  #geom_pointrange(data = comb_data_binned, aes(x = subage+.5, y = data_mean, ymin =data_ci_lower, ymax = data_ci_upper), stroke = 1, pch = 5)+
  #geom_line(data = comb_data_binned, aes(x = subage+.5, y = data_mean))+
  geom_line(data = plot_prag_exp, aes(x=age+2,y = pred, col = alignment, group = interaction(chain,iteration)), size = .2, alpha = .25)+
  geom_smooth(data = comb_data, aes(x = age_num, y = correct), col = "black", method = "glm", method.args = list(family = "binomial"), se = T, alpha = .4, lty = 2, size = 1)+
  labs(x="Age",y="Mutual Exclusivity effect")+
  facet_grid(alignment~item)+
  theme_few() +
  ylim(-0.05,1.05)+
  xlim(2,5)+
  guides(alpha = F, fill = F, col = F)+ 
  scale_colour_ptol(name = NULL)
```

```{r}
ggsave("../graphs/paper_figure3.png", width = 6, height = 2, scale = 1.5)
 ```

```{r}
plot_cor_model_exp <- readRDS( "../saves/corr_model_data_exp.rds")%>%
  filter(model == "integration")

plot_cor_exp <- ggplot(data = plot_cor_model_exp,aes(x = model_mean, y = data_mean, col = alignment)) +
  geom_abline(intercept = 0, slope = 1, lty = 2, alpha = 1, size = .5)+
  geom_errorbar(aes(ymin = data_ci_lower, ymax = data_ci_upper),width = 0,size = .5, alpha = .7)+
  geom_errorbarh(aes(xmin = model_ci_lower, xmax = model_ci_upper), height = 0,size = .5, alpha = .7)+
  geom_point(size = 1.5, stroke = 1, pch = 5)+
  coord_fixed()+
 stat_cor(method = "pearson", label.x = 0.01, label.y = 0.99, aes(x = model_mean, y = data_mean), inherit.aes = F, size = 3)+
  xlim(0,1)+ylim(0,1)+
  xlab("Model")+
  ylab("Data")+
  facet_grid(~age)+
  theme_few() + 
  scale_colour_ptol(name = "")
```

```{r}
ggarrange(
ggarrange(plot_speak_opt, plot_prior,plot_sem_know, labels = c("A","B","C"), nrow = 1, widths = c(1,1,1.5)),
ggarrange(pred_cor, labels = c("D"), nrow = 1 ),
nrow= 2,
heights = c(1,1)
)
```
